%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing


\begin{document}

\header{Jules}{ Scholler}{Junior Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
1 allée Django Reinhardt
94110, Arcueil
France
~
+33 687 853 626
~
\href{mailto:jules.scholler@gmail.com}{jules.scholler@gmail.com}
\section{Languages}
French: mother tongue
English: good skills \\ (TOEIC 965/990)
Spanish: intermediate skills
\section{Programming}
{\color{red} $\star\star\star$} Matlab
{\color{red} $\star\star$} C, Python \& ImageJ
{\color{red} $\star$} Mathematica \& \LaTeX
\section{About}
Car \& Motorbike driving licenses
First aid certificate
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------

\entry
{2016--2017}
{MSc {\normalfont Mathémathiques, Vision, Apprentissage}}
{École Normale Supérieure, Paris-Saclay}
{Specialization in image processing, computer vision and deep learning.}

\entry
{2013--2016}
{MSc{\normalfont-level Diplôme d’ingénieur ESPCI}}
{ESPCI Paris, PSL Research University}
{\emph{L'École Supérieure de Physique et de Chimie Industrielles de la Ville de Paris} is a major institute of higher education in science and engineering.\\ Specialization in Physics - Awarded with highest honors.}


%------------------------------------------------

\entry
{2010--2013}
{BSc {\normalfont in Physics and Chemistry}}
{UPEM, Marne la Vallée}
{Specialization in English - Awarded with high honors.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2016}
{Institut Langevin - Ref: ignacio.izeddin@espci.fr}
{Paris, France}
{\emph{Research Intern in Photonics - 4 months} \\
Project: using the STORM technique to map the local density of states (LDOS) on semi-random metallic substrate with a super-resolution. Main topics:
\begin{itemize}
\item Single photon counting \& Nanoprobe tracking
\item Image processing \& Multi-parameters non-linear fittings
\item Nano-precise feedback loops 
\item Software development (Matlab GUI) for complete automation and detectors controls
\end{itemize}}

\entry
{2015}
{Olympus NDT - Ref: jason.habermehl@olympus-ossa.com}
{Québec, Canada}
{\emph{R\&D Intern in non-destructive testing - 6 months} \\
	Project: pipelines tube testing using ultrasounds and development of a new innovative inspection method. Main topics:
	\begin{itemize}
\item Phased array ultrasound testing (linear and matrix arrays)
\item Signal processing, Interface computer machinery, Modeling \& Statistical studies
\item Full Matrix Capture (FMC) \& Total Focusing Method (TFM)
\item Inverse problem through interfaces \& Adaptive focusing
	\end{itemize}}
%------------------------------------------------

\end{entrylist}

\subsection{Part Time}

\begin{entrylist}

\entry
{2010--now}
{Anacours}
{Region of Paris, France}
{\emph{Teacher} \\
Private tuition in mathematics, physics and chemistry ($\sim$10h/week).}
\entry
{2014--2015}
{Student Government}
{Paris, France}
{\emph{Treasurer} \\
In charge of the budget and purchasing (>100k€/year). Managing relationships with banks. Team work.}


\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{entrylist}
	
	%------------------------------------------------
	
	\entry
	{2016}
	{Postgraduate Scholarship}
	{SAFRAN Group}
	{Awarded by SAFRAN Group for academical excellence and professional ambitions.}
	
	%------------------------------------------------
	
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\textbf{Professional:} Imaging, Wave propagation, Signal processing, AI, Applied research \\ \textbf{Personal:} New technology, Sports, Travels, Crime novels, Motorbike mechanics.


\end{document}